---
title: "Helping End Teddington"
format: markdown_github
include: false
---

This is a simple attempt to help narrow down the possible comedian-footballer pairs that Max could have chosen for his cursed Teddington Comedian/Footballer Quiz on [What Did You Do Yesterday](https://podcasts.apple.com/us/podcast/what-did-you-do-yesterday-with-max-rushden-david-odoherty/id1765600990).
Fellow listener @lindsayevanslee created an amazing [website](https://endteddingtonnow.com) for calculating the probability of seeing different comedian-footballer combinations. 

In the Midweek Mayhem from November 25 2025, Max and David were using the website and Max gave us a *huge* clue when he revealed that the combined probability of his comedian and footballer was *0.0001%*.
Since @lindsayevanslee has kindly made the [data and code available on GitHub](https://github.com/lindsayevanslee/end-teddington-now), we can use it to try and narrow down the possible pairs that Max could have chosen.

```{r}
library(tidyverse)

comedians <- read_csv(
  "https://raw.githubusercontent.com/lindsayevanslee/end-teddington-now/refs/heads/main/data/comedians_probability.csv"
) |>
  set_names(tolower)
footballers <- read_csv(
  "https://raw.githubusercontent.com/lindsayevanslee/end-teddington-now/refs/heads/main/data/footballers_probability.csv"
) |>
  set_names(tolower)

all <- cross_join(
  comedians,
  footballers,
  suffix = c("_comedian", "_footballer")
) |>
  mutate(
    combined_probability = probability_comedian * probability_footballer,
    rounded_probability = round(combined_probability * 100, 4)
  )
```

There are `{r} format(nrow(comedians), big.mark = ",")` comedians and `{r} format(nrow(footballers), big.mark = ",")` footballers in the data compiled by 
@lindsayevanslee. 
This means there are `{r} format(nrow(all), big.mark = ",")` possible comedian-footballer pairs. Max said on the show that the combined probability of his footballer and his comedian was 0.0001%. 

```{r}
all_filtered <- all |>
  filter(
    rounded_probability == 0.0001
  )

write_csv(all_filtered, "comedian_footballer_pairs_0001_percent.csv")
```

The [endteddingtonnow.com website](https://endteddingtonnow.com) rounds the combined probabilities to four decimal places, so we lose a bit of precision. 
If we filter the data to only include pairs with a rounded combined probability of 0.0001%, we find there are still `{r} format(nrow(all_filtered), big.mark = ",")` such pairs, which is not very useful.

```{r}
jordans <- all_filtered |>
  filter(name_footballer == "Jordan Henderson")
```

However, if we follow on DoD's and Mars Bar's suggestion to lock in Jordan Henderson as the footballer, we can see which comedians pair with him to give a combined probability of 0.0001%.
This gives us a much more reasonable list of `{r} nrow(jordans)` comedians. With one guess a week, we could get through this list in just over `{r} floor(nrow(jordans) / 52)` years!

### List of comedians paired with Jordan Henderson that give a combined probability of 0.0001%

```{r}
#| echo: false
#| include: true
jordans |>
  arrange(desc(probability_comedian)) |>
  knitr::kable()
```
